Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-22 sections/eval.tex
Update on Overleaf.

To get a sense of the Python Array API, we provide a few examples of their

@@

\begin{align*}
    \finchreorder(name, idxs...) := 
\end{align*}

>>>>

To get a sense of the Python Array API, we provide a few examples of required functions which we will then translate to Finch Logic statements.

@@

\begin{align*}
    \finchplan(queries...) &  \finchquery(name, expr) & \finchreorder(expr, idxs...)\\
    \finchrelabel(expr, idxs...)& \finchmapjoin(op, exprs...) & \finchaggregate(op, expr)\\
    & \finchtable(tns, idxs...) & \\
\end{align*}
